\documentclass[12pt,a4paper]{article}
\begin{document}
\title{FIREBASE AND GOOGLE CLOUD PLATFORM(GCP)}
\author{OCAN JOHN JOEL.\\
COURSE NAME: RESEARCH METHODOLOGY\\
   COURSE CODE:BIT2207\\
    REG NUMBER: 16/U/10705/ps.\\
      STUDENT NUMBER: 216009506\\}
\maketitle   
   Firebase helps one to build a better mobile apps and grow the business. Firebase products are backed by Google Cloud platform, letting one to scale his/her app to billions of users.
\section{Build apps fast, without managing infrastructure}
Firebase gives functionality like analytics, database, messaging and crash reporting so you can move quickly and focus on your users.
\section{Backed by google, trusted by top apps}
  Firebase is built on google infrastructure and scales automatically, for even the largest apps.
Firebase products work greatly individually but share data and insights, so they work even better together.
\section{products}
Firebase and GCP share two products: 
The cloud function and cloud storage. These are the same products that exit in cloud, simply exposed for client-server SDKs(Cloud) and the client SDKs (Firebase), so your frontend and backend teams can work in concert.
\section{Projects.}
Each account can have multiple projects, which are like folders or directories. Both Firebase and GCP products can be added to a project.

\begin{thebibliography}{100}

\bibitem{latexGuide}Doug steveson,Google cloud Developer,\\
Available at \texttt{https://www.quora.com/profile/Doug-Stevenson-1}.
\bibitem{latexMath}Supercharging Firebase with Google Cloud platform,\\
\texttt{https://www.youtube.com/watch?v=wOGfZ_aLGqM }
\end{thebibliography}
\end{document}

